\huge Modeling Intervention Strategies for TB Control in the United States

### 2013-07-26 in_progress/presentations/poster/reuMHC2013.tex
added caption for Incidence plot in beamer poster
added agentbased section to poster

          \caption{caption here!}

@@

        \begin{figure}[h]
          \begin{center}
            \includegraphics[scale=1]{EnLTBIRedGroupCost.pdf}
          \end{center}
          \caption{A graph of the cumulative implementation costs, savings, and 
                       net US health care system costs of reducing rates of LTBI in
                       Foreign-born arrivals by 50\%, 75\%, and 100\%.  To determine the 
                       implementation cost for each intervention, the average cost
                       to identify and treat entering Foreign-born individuals with LTBI
                       was set to be \$600, \$800, and \$1000 for the 50\%, 75\%, 
                       and 100\% reduction strategies respectively.}
          \label{fig:redEnLTBI_costs}
        \end{figure}
      \end{block}
    \end{column}
    \begin{column}{.3\textwidth}
      \begin{block}{An Agent Based Implementation}
        Implementing an Agent Based Framework
      \end{block}
    \end{column}
  \end{columns}
\end{frame}
\end{document}

>>>>

          \caption{A graph of the projected incidence levels per million in
                       the US-born, Foreign-born, and Total US population, given
                       that LTBI rates in Foreign-born arrivals are reduced by 
                       0\%, 50\%, 75\%, and 100\%.}

@@

        \begin{figure}[h]
          \begin{center}
            \includegraphics[scale=1]{EnLTBIRedGroupCost.pdf}
          \end{center}
          \caption{A graph of the cumulative implementation costs, savings, and 
                       net US health care system costs of reducing rates of LTBI in
                       Foreign-born arrivals by 50\%, 75\%, and 100\%.  To determine the 
                       implementation cost for each intervention, the average cost
                       to identify and treat entering Foreign-born individuals with LTBI
                       was set to be \$600, \$800, and \$1000 for the 50\%, 75\%, 
                       and 100\% reduction strategies respectively.}
          \label{fig:redEnLTBI_costs}
        \end{figure}
      \end{block}
    \end{column}
    \begin{column}{.3\textwidth}
      \begin{block}{An Agent Based Implementation}
        In addition to the extended Hill model (implemented in R), we also
        created a stochastic agent-based counterpart in both NetLogo and C++.
        Stochastic models add notions of uncertainty into the model structure,
        while agent-based models simulate global behavior of the system by
        describing local behavior of individual agents in the population.

        Figure~\ref{fig:NLHMinc} shows the incidence rate over time for both
        the R and NetLogo models. Although the NetLogo model is stochastic, its
        incidence rates roughly coincide with those given by the R model. With the
        C++ model (figure~\ref{fig:finalRun}), we obtain even better convergence.
        \begin{block}{}
          \begin{column}{.45\textwidth}
            \begin{figure}[h]
              \begin{center}
                \includegraphics[width=\textwidth]{NLHMinc}
              \end{center}
              \caption{Incidence per million for R and NetLogo models (12 runs)}
              \label{fig:NLHMinc}
            \end{figure}
          \end{column}
          \begin{column}{.45\textwidth}
            \begin{figure}[h]
              \begin{center}
                \includegraphics[width=\textwidth]{finalRunSmall}
              \end{center}
              \caption{Incidence per million for R and C++ models (2100 runs)}
              \label{fig:finalRun}
            \end{figure}
          \end{column}
        \end{block}
      \end{block}
    \end{column}
  \end{columns}
\end{frame}
\end{document}
